
\addcontentsline{toc}{section}{Список литературы}
\begin{thebibliography}{99}
    \bibitem{c1} 
    Steven Altschuler. Singularities of the curve shrinking flow for space curves. \textit{J. Differential Geometry}, 34:491–514, 1991.
    
    \bibitem{c2}
    Steven Altschuler and Matthew Grayson. Shortening space curves and flow through singularities. \textit{J. Differential Geom.}, 35:283–298, 1992.
    
    \bibitem{c3}
    Shigetoshi Bando. Real analyticity of solutions of Hamilton’s equation. \textit{Math. Z.}, 195(1):93–97, 1987.
    
    \bibitem{c4}
    Yu. Burago, M. Gromov, and G. Perel\`man. A. D. Aleksandrov spaces with curvatures bounded below. \textit{Uspekhi Mat. Nauk}, 47(2(284)):3–51, 222, 1992.
    
    \bibitem{c5}
    Huai-Dong Cao and Xi-Ping Zhu. A complete proof of the Poincaré and Geometrization conjectures – Application of the Hamilton-Perelman theory of the Ricci flow. \textit{Asian J. of Math}, 10:169–492, 2006.
    
    \bibitem{c6}
    Jeff Cheeger. Finiteness theorems for Riemannian manifolds. \textit{Amer. J. Math.}, 92:61–74, 1970.
    
    \bibitem{c7}
    Jeff Cheeger and David Ebin. Comparison theorems in Riemannian geometry. \textit{North-Holland Publishing Co.}, Amsterdam, 1975. North-Holland Mathematical Library, Vol. 9.
    
    \bibitem{c8}
    Jeff Cheeger and Detlef Gromoll. The structure of complete manifolds of nonnegative curvature. \textit{Bull. Amer. Math. Soc.}, 74:1147–1150, 1968.
    
    \bibitem{c9}
    Jeff Cheeger and Detlef Gromoll. The splitting theorem for manifolds of nonnegative Ricci curvature. \textit{J. Differential Geometry}, 6:119–128, 1971/1972.
    
    \bibitem{c10}
    Jeff Cheeger and Detlef Gromoll. On the structure of complete manifolds of nonnegative curvature. \textit{Ann. of Math. (2)}, 96:413–433, 1972.
    
    \bibitem{c11}
    Jeff Cheeger, Mikhail Gromov, and Michael Taylor. Finite propagation speed, kernel estimates for functions of the Laplace operator, and the geometry of complete Riemannian manifolds. \textit{J. Differential Geom.}, 17(1):15–53, 1982.
    
    \bibitem{c12}
    B. L. Chen and X. P. Zhu. Uniqueness of the Ricci flow on complete noncompact manifolds. \textit{math.DG/0505447}, 2005.
    
    \bibitem{c13}
    Bennett Chow and Dan Knopf. The Ricci flow: an introduction, volume 110 of Mathematical Surveys and Monographs. \textit{American Mathematical Society}, Providence, RI, 2004.
    
    \bibitem{c14}
    Bennett Chow, Peng Lu, and Li Ni. Hamilton\'s Ricci flow. to appear, 2006.
    
    \bibitem{c15}
    Tobias H. Colding and William P. Minicozzi, II. Estimates for the extinction time for the Ricci flow on certain 3-manifolds and a question of Perelman. \textit{J. Amer. Math. Soc.}, 18(3):561–569 (electronic), 2005.
    
    \bibitem{c16}
    Dennis M. DeTurck. Deforming metrics in the direction of their Ricci tensors. \textit{J. Differential Geom.}, 18(1):157–162, 1983.
    
    \bibitem{c17}
    Yu Ding. Notes on Perelman\'s second paper. Available at \texttt{www.math.lsa.umich.edu/\~{}lott/ricciflow/perelman.html}, 2004.
    
    \bibitem{c18}
    M. P. do Carmo. Riemannian Geometry. \textit{Birkhäuser}, Boston, 1993.
    
    \bibitem{c19}
    Klaus Ecker and Gerhard Huisken. Interior estimates for hypersurfaces moving by mean curvature. \textit{Invent. Math.}, 105:547–569, 1991.
    
    \bibitem{c20}
    Lawrence C. Evans and Ronald F. Gariepy. Measure theory and fine properties of functions. \textit{Studies in Advanced Mathematics. CRC Press}, Boca Raton, FL, 1992.
    
    \bibitem{c21}
    M. Gage and R. S. Hamilton. The heat equation shrinking convex plane curves. \textit{J. Differential Geom.}, 23(1):69–96, 1986.
    
    \bibitem{c22}
    Sylvestre Gallot, Dominique Hulin, and Jacques Lafontaine. \textit{Riemannian geometry}. Universitext. Springer-Verlag, Berlin, third edition, 2004.

    \bibitem{c23}
    R. E. Greene and H. Wu. Lipschitz convergence of Riemannian manifolds. \textit{Pacific J. Math.}, 131:119–141, 1988.

    \bibitem{c24}
    Detlef Gromoll and Wolfgang Meyer. On complete open manifolds of positive curvature. \textit{Ann. of Math. (2)}, 90:75–90, 1969.

    \bibitem{c25}
    Mikhael Gromov. Structures métriques pour les variétés riemanniennes, volume 1 of Textes mathématiques. CEDIC/Fernand Nathan, Paris, France, 1981.

    \bibitem{c26}
    Mikhael Gromov and H. Blaine Lawson, Jr. Positive scalar curvature and the Dirac operator on complete Riemannian manifolds. \textit{Inst. Hautes Etudes Sci. Publ. Math.}, 58:83–196, 1983.

    \bibitem{c27}
    Robert Gulliver and Frank David Lesley. On boundary branch points of minimizing surfaces. \textit{Arch. Rational Mech. Anal.}, 52:20–25, 1973.

    \bibitem{c28}
    Richard S. Hamilton. The inverse function theorem of Nash and Moser. \textit{Bull. Amer. Math. Soc. (N.S.)}, 7(1):65–222, 1982.

    \bibitem{c29}
    Richard S. Hamilton. Three-manifolds with positive Ricci curvature. \textit{J. Differential Geom.}, 17(2):255–306, 1982.

    \bibitem{c30}
    Richard S. Hamilton. Four-manifolds with positive curvature operator. \textit{J. Differential Geom.}, 24(2):153–179, 1986.

    \bibitem{c31}
    Richard S. Hamilton. The Ricci flow on surfaces. In \textit{Mathematics and general relativity} (Santa Cruz, CA, 1986), volume 71 of Contemp. Math., pages 237–262. Amer. Math. Soc., Providence, RI, 1988.

    \bibitem{c32}
    Richard S. Hamilton. The Harnack estimate for the Ricci flow. \textit{J. Differential Geom.}, 37(1):225–243, 1993.

    \bibitem{c33}
    Richard S. Hamilton. A compactness property for solutions of the Ricci flow. \textit{Amer. J. Math.}, 117(3):545–572, 1995.

    \bibitem{c34}
    Richard S. Hamilton. The formation of singularities in the Ricci flow. In \textit{Surveys in differential geometry, Vol. II} (Cambridge, MA, 1993), pages 7–136. Internat. Press, Cambridge, MA, 1995.

    \bibitem{c35}
    Richard S. Hamilton. Four-manifolds with positive isotropic curvature. \textit{Comm. Anal. Geom.}, 5(1):1–92, 1997.

    \bibitem{c36}
    Richard S. Hamilton. Non-singular solutions of the Ricci flow on three-manifolds. \textit{Comm. Anal. Geom.}, 7(4):695–729, 1999.

    \bibitem{c37}
    Robert Hardt and Leon Simon. Boundary regularity and embedded solutions for the oriented Plateau problem. \textit{Ann. of Math. (2)}, 110(3):439–486, 1979.

    \bibitem{c38}
    Allen Hatcher. \textit{Algebraic topology}. Cambridge University Press, Cambridge, 2002.

    \bibitem{c39}
    John Hempel. \textit{3-Manifolds}. Princeton University Press, Princeton, N. J., 1976. Ann. of Math. Studies, No. 86.

    \bibitem{c40}
    Stefan Hildebrandt. Boundary behavior of minimal surfaces. \textit{Arch. Rational Mech. Anal.}, 35:47–82, 1969.

    \bibitem{c41}
    T. Ivey. Ricci solitons on compact three-manifolds. \textit{Diff. Geom. Appl.}, 3:301–307, 1993.

    \bibitem{c42}
    Jürgen Jost. \textit{Two-dimensional geometric variational problems}. Pure and Applied Mathematics (New York). John Wiley \& Sons Ltd., Chichester, 1991. A Wiley-Interscience Publication.

    \bibitem{c43}
    Vatali Kapovitch. Perelman\`s stability theorem. \textit{math.DG/0703002}, 2007.

    \bibitem{c44}
    Bruce Kleiner and John Lott. Notes on Perelman\`s papers. \textit{math.DG/0605667}, 2006.

    \bibitem{c45}
    O. A. Ladyzhenskaja, V. A. Solonnikov, and N. N. Ural\`ceva. \textit{Linear and quasilinear equations of parabolic type}. Translated from the Russian by S. Smith. Translations of Mathematical Monographs, Vol. 23. American Mathematical Society, Providence, R.I., 1967.

    \bibitem{c46}
    Peter Li and L-F. Tam. The heat equation and harmonic maps of complete manifolds. \textit{Invent. Math.}, 105:305–320, 1991.

    \bibitem{c47}
    Peter Li and Shing-Tung Yau. On the parabolic kernel of the Schrödinger operator. \textit{Acta Math.}, 156(3-4):153–201, 1986.

    \bibitem{c48}
    Peng Lu and Gang Tian. Uniqueness of standard solutions in the work of Perelman. Available at \texttt{www.math.lsa.umich.edu/\~lott/ricciflow/StanUniqWork2.pdf}, 2005.

    \bibitem{c49}
    John Milnor. Towards the Poincaré conjecture and the classification of 3-manifolds. \textit{Notices Amer. Math. Soc.}, 50(10):1226–1233, 2003.

    \bibitem{c50}
    J. Morgan and G. Tian. Completion of Perelman\'s proof of the Geometrization Conjecture. In preparation, 2007.

    \bibitem{c51}
    C. B. Morrey. The problem of Plateau on a Riemannian manifold. \textit{Ann. Math.}, 49:807–851, 1948.

    \bibitem{c52}
    G. Perelman. The entropy formula for the Ricci flow and its geometric applications. math.DG/0211159, 2002.

    \bibitem{c53}
    G. Perelman. Finite extinction time for the solutions to the Ricci flow on certain three-manifolds. math.DG/0307245, 2003.

    \bibitem{c54}
    G. Perelman. Ricci flow with surgery on three-manifolds. math.DG/0303109, 2003.

    \bibitem{c55}
    S. Peters. Convergence of Riemannian manifolds. \textit{Compositio Math.}, 62:3–16, 1987.

    \bibitem{c56}
    P. Petersen. \textit{Riemannian geometry, Second Edition}, volume 171 of Graduate Texts in Mathematics. Springer-Verlag, New York, 2006.

    \bibitem{c57}
    H. Poincaré. Cinquième complément à l\'analyse situs. In \textit{Œuvres. Tome VI, Les Grands Classiques Gauthier-Villars}, pages v+541. Editions Jacques Gabay, Sceaux, 1996. Reprint of the 1953 edition.

    \bibitem{c58}
    J. Sacks and K. Uhlenbeck. The existence of minimal immersions of 2-spheres. \textit{Ann. of Math.}, 113:1–24, 1981.

    \bibitem{c59}
    T. Sakai. \textit{Riemannian geometry}, volume 149 of Translations of Mathematical Monographs. American Mathematical Society, Providence, RI, 1996. Translated from the 1992 Japanese original by the author.

    \bibitem{c60}
    R. Schoen and S.-T. Yau. \textit{Lectures on differential geometry}. Conference Proceedings and Lecture Notes in Geometry and Topology, I. International Press, Cambridge, MA, 1994.

    \bibitem{c61}
    R. Schoen and S.-T. Yau. The structure of manifolds with positive scalar curvature. In \textit{Directions in partial differential equations (Madison, WI, 1985)}, volume 54 of Publ. Math. Res. Center Univ. Wisconsin, pages 235–242. Academic Press, Boston, MA, 1987.

    \bibitem{c62}
    P. Scott. The geometries of 3-manifolds. \textit{Bull. London Math. Soc.}, 15(5):401–487, 1983.

    \bibitem{c63}
    N. Sesum, G. Tian, and X.-D. Wang. Notes on Perelman\'s paper on the entropy formula for the Ricci flow and its geometric applications. preprint, 2003.

    \bibitem{c64}
    W.-X. Shi. Deforming the metric on complete Riemannian manifolds. \textit{J. Differential Geom.}, 30(1):223–301, 1989.

    \bibitem{c65}
    W.-X. Shi. Ricci deformation of the metric on complete noncompact Riemannian manifolds. \textit{J. Differential Geom.}, 30(2):303–394, 1989.

    \bibitem{c66}
    T. Shioya and T. Yamaguchi. Volume collapsed three-manifolds with a lower curvature bound. \textit{Math. Ann.}, 333(1):131–155, 2005.

    \bibitem{c67}
    J. Stallings. A topological proof of Gruschko\'s theorem on free products. \textit{Math. Z.}, 90:1–8, 1965.

    \bibitem{c68}
    W. P. Thurston. Hyperbolic structures on 3-manifolds. I. Deformation of acylindrical manifolds. \textit{Ann. of Math. (2)}, 124(2):203–246, 1986.

    \bibitem{c69}
    V. Toponogov. Spaces with straight lines. \textit{AMS Translations}, 37:287–290, 1964.

    \bibitem{c70}
    B. White. Classical area minimizing surfaces with real-analytic boundaries. \textit{Acta Math.}, 179(2):295–305, 1997.

    \bibitem{c71}
    R. Ye. On the l function and the reduced volume of Perelman. Available at www.math.ucsb.edu/\~yer/reduced.pdf, 2004.

\end{thebibliography}